From clusters to queries: exploiting uncertainty in the modular landscape of complex networks

### 2018-03-16 article/article.tex
More job script bugs

One example of community detection that has gained significant interest is in systems biology \cite{}.
A core goal here is to characterise the function and functional relationships between genes, proteins or metabolites within a larger network.
In many situations, only the role of a small number of genes is known, with much of the annotation for a given organism being computed through naive homology information that ignores the role of a gene within a wider context.
The advent of high throughput experimental datasets has allowed the construction of genome scale networks, leading to the observation of non-trivial topological properties such as densely connected clusters \cite{ArabidopsisConsortium2011}.
These densely connected clusters are widely believed to be associated with specific function, such as protein complexes or biochemical pathways \cite{}.

>>>>

The use of community detection is widespread.
For example, core goal in systems biology is to characterise the function and functional relationships between genes, proteins or metabolites within a larger network \cite{}.
In many situations, only the role of a small number of genes is known, with much of the annotation for a given organism being computed through naive homology information that ignores the role of a gene within a wider context.
The advent of high throughput experimental datasets has allowed the construction of genome scale networks, leading to the observation of non-trivial topological properties such as densely connected clusters \cite{ArabidopsisConsortium2011}.
These densely connected clusters are widely believed to be associated with specific function, such as protein complexes or biochemical pathways \cite{}.
